plots with prolactin

### 2020-01-27 analysis/16_PRL.Rmd
new data csv

```{r}
write.csv(candidates.pit, "../results/16_pitPRL.csv")
write.csv(aov_all, "../results/16_aov_PRLsex.csv")
write.csv(aov_manip, "../results/16_aov_PRLsextreatment.csv")
```

>>>>

## music for own

```{r}
meanBrcaPrl <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment, sex) %>%
  dplyr::summarise(meanBRCA1 = mean(BRCA1), 
                   meanPRL = mean(PRL)) %>%
  dplyr::mutate(meanBRCA1 = round(meanBRCA1,2)) %>%
  dplyr::mutate(meanPRL = round(meanPRL,1)) %>%
  dplyr::filter(treatment %in% charlevels) %>%
  droplevels() %>%
  dplyr::mutate(timepoint = as.numeric(treatment)) %>%
  select(timepoint, treatment, sex, meanPRL, meanBRCA1)
meanBrcaPrl
summary(meanBrcaPrl)
```

```{r}
write.csv(candidates.pit, "../results/16_pitPRL.csv")
write.csv(aov_all, "../results/16_aov_PRLsex.csv")
write.csv(aov_manip, "../results/16_aov_PRLsextreatment.csv")
write.csv(meanBrcaPrl, "../results/16_meanBrcaPrl.csv", row.names = F)
